---
title: "p8105_hw1_xy2719"
author: "Yao"
date: "2025-09-19"
output: github_document
---

## Problem 1
```{r echo=TRUE}
# Load the tidyverse and moderndive library
library(tidyverse)
library(moderndive)

# Load the 'early_january_weather' dataset
data("early_january_weather")

# View the dataset
view(early_january_weather)
```

```{r echo=TRUE}
# Accessing the dataset help file
?early_january_weather

# Get the size of the dataset and the mean of temperature
nrow(early_january_weather)
ncol(early_january_weather)
round(mean(early_january_weather$temp), 1)
```
The 'early_january_weather' dataset contains hourly meteorological data for LGA, JFK and EWR for the month of January 2013. This subset data frame contains hourly weather data of EWR.
This dataset includes `r nrow(early_january_weather)` rows, `r ncol(early_january_weather)` columns, and 15 variables. The important variables are 'origin', 'year', 'month', 'day', 'hour', 'temp', 'demp', 'humid', 'wind_dir', wind_speed', wind_gust', 'precip', 'pressure', 'visib', and 'time_hour'.
The mean temperature during this period was **`r round(mean(early_january_weather$temp, na.rm = TRUE), 1)` °F**.

```{r echo=TRUE}
# Create a scatterplot of temp (y) vs time_hour (x)
scatter_temp_time = ggplot(early_january_weather,
                           aes(x = time_hour, y = temp, color = humid)) +
  geom_point() +
  labs(x = "Time(Hour)", y = "Temperature(°F)",
       title = "EWR Weather: Temperature vs Time ",
       color = "Humidity") +
  theme_minimal()

# Print the scatterplot
scatter_temp_time

# Save the scatterplot
ggsave("scatter_temp_time.png", scatter_temp_time, width = 7, height = 4)
```
The scatterplot shows hourly temperature change over time, with points showing different humidity levels. Temperature goes up and down during the day, following a daily cycle. Temperatures are generally cooler when humidity is higher, and warmer when humidity is lower.
